---
title: "jessica_personal"
author: "Shiwei Chen"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(gganimate)
library(gifski)
library(png)
library(plotly)
library(ggplot2)
library(readr)
library(readxl)
library(patchwork)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r, include=FALSE}
# Import and clean data
df20_tidy = 
  read_csv("../data/2020data.csv") %>% 
  janitor::clean_names() %>%
  select(-1, -precinct_of_crime, -ky_cd, -description_of_crime, -pd_desc, -pd_cd, -description_of_premises, -juris_desc, -jurisdiction_code, -parks_nm, -hadevelopt, -transit_district, -latitude, -longitude, -lat_lon, -station_name)
  
```

# Data Visualization
### Suspect plot{.tabset}

```{r}
susp_df = df20_tidy %>% 
  select(susp_age_group, susp_race, susp_sex) %>% 
  filter(!is.na(.)) %>% 
  filter(!(susp_age_group == "UNKNOWN"), 
         !(susp_race == "UNKNOWN"), 
         !(susp_sex == "UNKNOWN"), 
         !(susp_sex == "U"))



susp_age =
  susp_df %>% 
  group_by(susp_age_group) %>% 
  summarise(count = n()) %>% 
  filter(susp_age_group == "<18" | susp_age_group == "18-24" | susp_age_group == "25-44" | susp_age_group == "45-64" | susp_age_group == "65+") %>% 
  ggplot(
    aes(x = susp_age_group, y = count, color = susp_age_group, fill = susp_age_group)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Age group",
    y = "Number of people",
    title = "Total number of people in each age group(Suspect)"
  )


susp_race =
  susp_df %>% 
  group_by(susp_race) %>% 
  summarise(count = n()) %>% 
  mutate(susp_race = factor(susp_race), 
         susp_race = fct_reorder(susp_race, count)) %>%
  ggplot(
    aes(x = susp_race, y = count, color = susp_race, fill = susp_race)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Race",
    y = "Number of people",
    title = "Total number of people for each race(Suspect)"
  ) +
  theme(
      axis.text.x = element_text(angle = 270, vjust = 0.5, hjust = 0.5),
      legend.position = "none")


susp_sex = 
  susp_df %>% 
  group_by(susp_sex) %>% 
  summarise(count = n()) %>% 
   ggplot(
    aes(x = susp_sex, y = count, color = susp_sex, fill = susp_sex)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Sex",
    y = "Number of people",
    title = "Total number of people in each sex group(Suspect)"
  ) 


susp_agexrace = 
  susp_df %>% 
  group_by(susp_age_group, susp_race) %>% 
  summarise(number_of_people = n()) %>% 
  filter(susp_age_group == "<18" | susp_age_group == "18-24" | susp_age_group == "25-44" | susp_age_group == "45-64" | susp_age_group == "65+") %>% 
   ggplot(
    aes(x = susp_age_group, y = number_of_people, color = susp_race, fill = susp_race)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Age group",
    y = "Number of people",
    title = "Total number of people in each age group with race(Suspect)"
  )


susp_agexsex = 
  susp_df %>% 
  group_by(susp_age_group, susp_sex) %>% 
  summarise(number_of_people = n()) %>% 
  filter(susp_age_group == "<18" | susp_age_group == "18-24" | susp_age_group == "25-44" | susp_age_group == "45-64" | susp_age_group == "65+") %>% 
   ggplot(
    aes(x = susp_age_group, y = number_of_people, color = susp_sex, fill = susp_sex)
    ) + 
  geom_bar(stat = "identity") +
  labs(
    x = "Age group",
    y = "Number of people",
    title = "Total number of people in each age group with sex(Suspect)"
  )


susp_racexsex = 
  susp_df %>% 
  group_by(susp_race, susp_sex) %>% 
  summarise(number_of_people = n()) %>%
  mutate(susp_race = factor(susp_race), 
         susp_race = fct_reorder(susp_race, number_of_people)) %>%
  ggplot(
    aes(x = susp_race, y = number_of_people, color = susp_sex, fill = susp_sex)
    ) + 
  geom_bar(stat = "identity") +
  labs(
    x = "Race",
    y = "Number of people",
    title = "Total number of people for each race with sex(Suspect)"
  ) +
  theme(
      axis.text.x = element_text(angle = 270, vjust = 0.5, hjust = 0.5),
      legend.position = "none")

```


#### Age
```{r}
susp_age
```


#### Race
```{r}
susp_race
```


#### Sex
```{r}
susp_sex
```


#### Age x Race
```{r}
susp_agexrace
```


#### Age x Sex
```{r}
susp_agexsex
```


#### Race x Sex
```{r}
susp_racexsex
```






### Victim plot
```{r}
vic_df = df20_tidy %>% 
  select(vic_age_group, vic_race, vic_sex) %>% 
  filter(!is.na(.)) %>% 
  filter(!(vic_age_group == "UNKNOWN"), !(vic_race == "UNKNOWN"), !(vic_sex == "UNKNOWN"), !(vic_sex == "U")) %>% 
  filter(vic_age_group == "<18" | vic_age_group == "18-24" | vic_age_group == "25-44" | vic_age_group == "45-64" | vic_age_group == "65+") %>% 
  filter(vic_sex == "F" | vic_sex == "M")
```

1. victim-age plot(Total number of people in each age group(Victim))

```{r}
vic_df %>% 
  group_by(vic_age_group) %>% 
  summarise(count = n()) %>% 
   ggplot(
    aes(x = vic_age_group, y = count, color = vic_age_group, fill = vic_age_group)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Age group",
    y = "Number of people",
    title = "Total number of people in each age group(Victim)"
  )
```

Conclusion: In 2020, persons between the ages of 25 and 44 have the highest victimization rates for all types of crime, while those age 65 or older have the lowest.



2. victim-race plot(Total number of people for each race(Victim))

```{r}
vic_df %>% 
  group_by(vic_race) %>% 
  summarise(count = n()) %>% 
  mutate(vic_race = factor(vic_race), 
         vic_race = fct_reorder(vic_race, count)) %>%
   ggplot(
    aes(x = vic_race, y = count, color = vic_race, fill = vic_race)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Race",
    y = "Number of people",
    title = "Total number of people for each race(Victim)"
  ) +
  theme(
      axis.text.x = element_text(angle = 270, vjust = 0.5, hjust = 0.5),
      legend.position = "none")
```

Conclusion: In 2020, persons with black race have the highest victimization rates for all types of crime, while native american have the lowest.



3. victim-sex plot(Total number of people in each sex group(Victim))

```{r}
vic_df %>% 
  group_by(vic_sex) %>% 
  summarise(count = n()) %>% 
  ggplot(
    aes(x = vic_sex, y = count, color = vic_sex, fill = vic_sex)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Sex",
    y = "Number of people",
    title = "Total number of people in each sex group(Victim)"
  )
```

Conclusion: In 2020, female have the highest victimization rates for all types of crime, but the victimization rates of both gender are similar.



4. victim-age x race plot(Total number of people in each age group with race(Victim))

```{r}
vic_df %>% 
  group_by(vic_age_group, vic_race) %>% 
  summarise(number_of_people = n()) %>%
  ggplot(
    aes(x = vic_age_group, y = number_of_people, color = vic_race, fill = vic_race)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Age group",
    y = "Number of people",
    title = "Total number of people in each age group with race(Victim)"
  )
```

Conclusion: In 2020, persons from 25 to 44 with black race have the highest victimization rates for all types of crime, while persons who younger than 18 with race of native american have the lowest.


5. victim-age x sex plot(Total number of people in each age group with sex(Victim))

```{r}
vic_df %>% 
  group_by(vic_age_group, vic_sex) %>% 
  summarise(number_of_people = n()) %>% 
  ggplot(
    aes(x = vic_age_group, y = number_of_people, color = vic_sex, fill = vic_sex)
    ) + 
  geom_bar(stat = "identity") +
  labs(
    x = "Age group",
    y = "Number of people",
    title = "Total number of people in each age group with sex(Victim)"
  )
```

Conclusion: In 2020, female from 25 to 44 have the highest victimization rates for all types of crime, while male who younger than 18 with race of native american have the lowest.



6. victim-race x age plot(Total number of people for each race with sex(Victim))

```{r}
vic_df %>% 
  group_by(vic_race, vic_sex) %>% 
  summarise(number_of_people = n()) %>%
  ggplot(
    aes(x = vic_race, y = number_of_people, color = vic_sex, fill = vic_sex)
    ) + 
  geom_bar(stat = "identity") +
  labs(
    x = "Race",
    y = "Number of people",
    title = "Total number of people for each race with sex(Victim)"
  ) +
  theme(
      axis.text.x = element_text(angle = 270, vjust = 0.5, hjust = 0.5),
      legend.position = "none")
```

Conclusion: In 2020, female with black race have the highest victimization rates for all types of crime, while female with race of native american have the lowest.



### Level of offense

```{r}
level_of_offense_df = 
  df20_tidy %>% 
  select(month, day, year, level_of_offense, name_of_borough, susp_age_group, susp_race, susp_sex) %>% 
  filter(!is.na(.)) %>% 
  filter(!(susp_age_group == "UNKNOWN"), 
         !(susp_race == "UNKNOWN"), 
         !(susp_sex == "UNKNOWN"), 
         !(susp_sex == "U"), 
         !(name_of_borough == " ")) %>%   
  filter(susp_age_group == "<18" | susp_age_group == "18-24" | susp_age_group == "25-44" | susp_age_group == "45-64" | susp_age_group == "65+")
```

```{r}
# 2020 level_of_offense by month,table and gif
level_of_offense_df %>% 
  group_by(month, level_of_offense) %>% 
  summarise(total_activity = n()) %>% 
  pivot_wider(
  names_from = "month", 
  values_from = "total_activity") %>% 
  knitr::kable()
```

```{r}
# Count of offense events in each month
level_of_offense_df %>%
  mutate(level_of_offense = as.factor(level_of_offense),
         month = as.integer(month)) %>% 
  group_by(month, level_of_offense) %>% 
  summarise(count = n()) %>%
  mutate(count = as.double(count)) %>% 
  ggplot(aes(x = month, y = count, color = level_of_offense)) + 
  geom_point() + geom_line() +
  transition_reveal(month) +
  labs(
    x = "Month",
    y = "Count",
    title = "Count of offense events in each month"
  ) +
  scale_x_continuous(
    breaks = c(0, 2, 4, 6, 8, 10, 12), 
    labels = c(0, 2, 4, 6, 8, 10, 12)
  )
```

Conclusion: From the gif related to the level of offense, we can see misdemeanor happen the most, while violation happen the least. In addition, January has the highest incidence of all types of crime, while April has the lowest incidence.



```{r}
# level_of_offense by district
level_of_offense_df %>%
  group_by(name_of_borough, level_of_offense) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = name_of_borough, y = count, color = level_of_offense, fill = level_of_offense)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Borough",
    y = "Count",
    title = "Count of offense events in each borough"
  ) +
  theme(
      axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.5),
      legend.position = "none")
```

Conclusion: The borough of bronx, brooklyn, and manhattan have a similarly high crime rate of all three types of offense events. The staten island has the lowest rate of all three types of crimes.



```{r}
# level_of_offense by age
level_of_offense_df %>%
  group_by(susp_age_group, level_of_offense) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = susp_age_group, y = count, color = level_of_offense, fill = level_of_offense)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Age group",
    y = "Count",
    title = "Count of offense events for each age group"
  )
```

Conclusion: Persons between the ages of 25 to 44 have the highest crime rates for all types of offense events, while those age 65 or older have the lowest.



```{r}
# level_of_offense by race
level_of_offense_df %>%
  group_by(susp_race, level_of_offense) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = susp_race, y = count, color = level_of_offense, fill = level_of_offense)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Race",
    y = "Count",
    title = "Count of offense events by race"
  ) +
  theme(
      axis.text.x = element_text(angle = 270, vjust = 0.5, hjust = 0.5),
      legend.position = "none")
```

Conclusion: Black race have the highest crime rates for all types of offense events, while native american have the lowest.



```{r}
# level_of_offense by sex
level_of_offense_df %>%
  group_by(susp_sex, level_of_offense) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = susp_sex, y = count, color = level_of_offense, fill = level_of_offense)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Sex",
    y = "Count",
    title = "Count of offense events by sex"
  )
```

Conclusion: Male have the highest crime rates for all types of offense events.

